Co-citations in context

### 2019-06-13 cocit_r.tex
lots of edits, look for blue text

\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research. The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies). Expected co-citation values were generated from Monte Carlo simulations under a random graph model. Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}. Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references. For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article. Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible. The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'

Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions. The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the \textcolor{blue}{disciplinary composition of the references cited in these publications}. However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.
Thus, in particular,  subject matter and  citation count do not impact the probability that the reference will be cited, so that  a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology. Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}. In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.  Accordingly, model misspecification is likely to arise on account of the simulated values not modeling the empirical data very well.

@@

Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature (the WoS superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
In other words, the concerns raised above about misspecification resulting from treating
all references as equiprobable, independent of discipline, apply to \cite{boyack_vs_uzzi_2014} as well.
 We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation subnetwork,   rather than all of WoS, would reduce model misspecification.  Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}. Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.

Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model misspecification compared to treating all substitutions within WoS as equiprobable. 
Furthermore, re-analyses of these three semantically-themed
 citation networks  under the improved model reveals strikingly different trends than those 
 observed by Uzzi {\em et al.} 
 For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established. Specifically, 
 HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.  Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism). 
 Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns. Overall, our study, although limited to three disciplinary subnetworks, suggests that co-citation analysis that inadequately considers disciplinary differences, may not be very useful at detecting universal features of impactful publications.

@@

To consider the relationship between citation impact, conventionality, and novelty we calculated percentiles for the number of accumulated citations in the first 8 years since publication for each article we studied and stratified. We also investigated multiple definitions of hit articles with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles. \textcolor{blue}{ Also, mention different thresholds, 1st and 10th, for novelty threshold.}

@@

\subsection{Model Misspecification and the Attributes of Disciplinary Context} A source of misspecification in the Uzzi {\em et al.}~model arises from not accounting for disciplinary heterogeneity by treating all references as equiprobable substituents. Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline. 
If the Uzzi {\em et al.} model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

@@

To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. The two largest of these research areas are \textcolor{blue}{physical sciences and life sciences and biomedicine}, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest. \textcolor{blue}{While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.}
Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine. In other words, the empirical data shows a strong tendency of publications to cite papers that are in the same major research area rather than in some other research area.  Thus, there is a strong bias towards citations that are {\em intra-network}. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006). Furthermore, these findings argue that a discipline-indifferent random graph model would exhibit misspecification (in deviating substantially from the empirical data), and supports the  concern about definitions of  innovation and conventionality that are based on deviation from expected values.

\begin{figure}%[tbhp]
\centering
\includegraphics[width=0.6\linewidth]{background-effect}     
\caption{\ Intra-network citation shuffling preserves the disciplinary composition of references. Publications of type Article belonging to the three disciplinary networks (Applied Physics, Immunology, and  Metabolism) were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (\textcolor{blue}{bg\_local}) or references from all articles in WoS (\textcolor{blue}{bg\_allWoS}). Citation shuffling was performed using either our algorithm (\emph{repcs})
 or that of Uzzi et al.~(\emph{umsj}). The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as a fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer. A fold difference of $1$ indicates that citation shuffling did not alter disciplinary composition. Data are shown for articles published in 1985. All eight boxplots are generated from 153 observations each. Null values were set to $1$. Note y-axis: $log_2$ scale.} 
\label{fig:be}
\end{figure}

@@

\begin{table}[ht]
\caption{Model misspecification is reduced by constraining substitutions to disciplinary subnetworks. For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (\textcolor{blue}{applied\_physics}, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background). K-L divergence was calculated using the R seewave package \citep{seewave2008}.  The reduction in K-L divergence between simulated and observed data  shows that model misspecification is reduced by  restricting the reference substitutions to the disciplinary subnetwork (our model), as compared to treating all substitutions within WoS as equiprobable.
}
\label{tab:kld}
\centering
\begin{tabular}{| ccccc |} 
  \hline
 Disciplinary Network & Year & Background & K-L Divergence & Ratio \\ 
  \hline
 appl\_physics & 1985 & appl\_physics & 1.21 &  \\ 
  & 1985 & all\_wos & 2.37 & 1.96 \\ 
  & 1995 & appl\_physics & 0.86 &  \\ 
  & 1995 & all\_wos & 2.37 & 2.77 \\ 
  & 2005 & appl\_physics & 0.95 &  \\ 
  & 2005 & all\_wos & 2.35 & 2.47 \\ 
    \hline
  immunology & 1985 & immunology & 0.75 &  \\ 
  & 1985 & all\_wos & 1.68 & 2.24 \\ 
   & 1995 & immunology & 0.78 &  \\ 
   & 1995 & all\_wos & 1.70 & 2.19 \\ 
   & 2005 & immunology & 0.73 &  \\ 
  & 2005 & all\_wos & 1.92 & 2.63 \\ 
    \hline
 metabolism & 1985 & metabolism & 1.11 &  \\ 
   & 1985 & all\_wos & 2.24 & 2.02 \\ 
  & 1995 & metabolism & 1.07 &  \\ 
  & 1995 & all\_wos & 2.33 & 2.17 \\ 
     & 2005 & metabolism & 1.19 &  \\ 
   & 2005 & all\_wos & 2.60 & 2.18 \\ 
   \hline
\end{tabular}
\end{table}

 We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.  The results (Table \ref{tab:kld}) confirm this prediction: simulations \textcolor{blue}{under the constrained model (which constrains substitutions to the
disciplinary subnetwork)} consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable. Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (ratios range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases).
These results clearly demonstrate that constraining reference substitutions to the given disciplinary network better models the observed data.

@@

Since the constrained model better fits the observed data, we evaluated the distribution of 
highly cited articles  (i.e., ``hit articles")
 in the four categories (HCHN, LCHN, HCLN, LCLN), for different
thresholds for hit articles.
Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category. 
The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency. 
However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),
and the highest hit rates for the 1995 applied physics datasets are in the 
HNLC category for both the top 1\% and top 10\% of all cited articles.  
%Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}). 
 Thus, the category exhibiting the highest hit rate \textcolor{blue}{(among highly cited papers)} depends on the
specific disciplinary network and to some extent on the \textcolor{blue}{threshold for being highly cited}.
 %was the case with immunology. 
Furthermore, the categories displaying the greatest hit rate vary 
to some extent % with parameter settings and 
with the year  \textcolor{blue}{(data not shown)}.
%The lack of stable results across parameter settings suggests that parameters must be selected judiciously.

\textcolor{blue}{I did not review the next two paragraphs.  I did--JRB}

@@

We also tested the explanatory power of each framework dimension by classifying articles as %Low Novelty (
LN %)
 or 
% High Novelty (
HN
%)
 and, separately, as 
% having Low Conventionality (
LC
%) 
or 
%High Conventionality (
HC. 
%)
We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.  That null hypothesis was rejected for the WoS data along both dimensions. Consistent with the findings in~\cite{uzzi_atypical_2013}, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and also overrepresented in the HN category at a $p<0.001$ in all but two cases: the p-values in those exceptions were $0.002$ and $0.007$.  
Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS. \textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.  Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$. These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, (3) novelty is more strongly related with hits in applied physics than is conventionality. More generally, we find that the dimensions most strongly related with hit articles vary between disciplinary and broad data sets, and also among disciplines.

@@

\emph{needs to be expanded}

Our study shows strong evidence that constraining the model to a disciplinary subnetwork reduces model misspecification. Furthermore,  using the constrained model instead of the unconstrained model to redefine high (or low) novelty and conventionality produces different trends, depending on the subnetwork. In particular, while Uzzi {\em et al.} found that highly cited papers were most likely to be
in the HNHC category, this observation does not consistently hold when using the improved model. Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research. 
In particular,  high novelty (as defined by Uzzi {\em et al.}) is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}). More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data.

\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} We described concerns with model misspecification at the outset along two general dimensions: the background dataset and sampling methodology for the random graph. The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology through the article z-score distributions. When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles. We thought it important to determine the extent to which each of our methodological differences contributed to our observations.  We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.  In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used and x\% z-scores changed signs in the case of the immunology dataset. \textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.

Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN. \textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.  However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.  More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand.

>>>>

\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research. The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies). Expected co-citation values were generated from Monte Carlo simulations under a random graph model. Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}. Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references. For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article. 
%\textcolor{blue}{Note that Uzzi et al. reported on the 10th percentile in the paper, but investigated many other definitions of novelty in the supplemental paper.  Should this be noted? Perhaps not for sake of brevity and we are citing just the main paper here.} 
Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible. The authors observed that HCHN articles were twice as likely to be highly cited \textcolor{blue}{compared to the background rate}, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.' 
%\textcolor{blue}{Should we be more precise here in using 'twice?'  Uzzi et al. say twice the background rate whereas this might be construed as twice the rate of other categories which is a much different thing.}

Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions. The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references. However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.
Thus, in particular,  subject matter and  citation count do not impact the probability that the reference will be cited, so that  a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology. Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}. In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.  Accordingly, model misspecification is likely to arise on account of the simulated values not modeling the empirical data very well.

@@

Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature (the WoS superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
In other words, the concerns raised above about misspecification resulting from treating
all references as equiprobable, independent of discipline, apply to \cite{boyack_vs_uzzi_2014} as well.
 We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation subnetwork  \textcolor{blue}{(i.e., the ``local network")}  rather than all of WoS
 \textcolor{blue}{ (the ``global network") } would reduce model misspecification.  
 Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}. Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.

Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the \textcolor{blue}{local network}  reduces model misspecification compared to 
the \textcolor{blue}{unconstrained model} that \textcolor{blue}{uses the global network, WoS, and treats all substitutions within WoS as equiprobable.} 
Furthermore, re-analyses of these three semantically-themed
 citation networks  under the improved model reveals strikingly different trends than
 when using all of WoS. 
 For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established. 
 Specifically, 
 HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.  Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism). 
 Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns. Overall, our study, although limited to three disciplinary subnetworks, suggests that co-citation analysis that inadequately considers disciplinary differences, may not be very useful at detecting universal features of impactful publications.

@@

To consider the relationship between citation impact, conventionality, and novelty we calculated percentiles for the number of accumulated citations in the first 8 years since publication for each article we studied and stratified. We also investigated multiple definitions of hit articles, with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles, and \textcolor{blue}{ 1st and 10th percentiles as thresholds for high novelty}. % \textcolor{blue}%{ Also, mention different thresholds, 1st and 10th, for novelty threshold.}

@@

\subsection{Model Misspecification and the Attributes of Disciplinary Context} 
A source of misspecification in the global model arises from not accounting for disciplinary heterogeneity by treating all references  \textcolor{blue}{within WoS} as equiprobable substituents. Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline. 
If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

@@

To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. The two largest of these research areas are physical sciences and life sciences \& biomedicine, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest. \textcolor{blue}{While there is some variability over the years, under the unconstrained model, we would expect close to 35\% of the references cited by the publications in any large network  to be drawn from the physical sciences and close to 63\% of the references to be drawn from  life sciences and biomedicine.}
Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine. In other words, the empirical data shows a strong tendency of publications to cite papers that are in the same major research area rather than in some other research area.  Thus, there is a strong bias towards citations that are {\em intra-network}. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006). Furthermore, these findings argue that a discipline-indifferent random graph model would exhibit misspecification (in deviating substantially from the empirical data), and supports the  concern about definitions of  innovation and conventionality that are based on deviation from expected values.

\begin{figure}%[tbhp]
\centering
\includegraphics[width=0.6\linewidth]{background-effect}     
\caption{\textcolor{blue}{ Citation shuffling using the local network preserves the disciplinary composition of references within subnetworks, but using the global network does not.}   Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary subnetwork. Citation shuffling was performed using either our algorithm (\emph{repcs}, top row)
 or that of Uzzi et al.~(\emph{umsj}, bottom row).
 The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as a fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer. A fold difference of $1$ indicates that citation shuffling did not alter disciplinary composition. Data are shown for articles published in 1985. All eight boxplots are generated from 153 observations each. Null values were set to $1$. Note y-axis: $log_2$ scale.} 
\label{fig:be}
\end{figure}

@@

\begin{table}[ht]
\caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary subnetworks. For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background). K-L divergence was calculated using the R seewave package \citep{seewave2008}.  The reduction in K-L divergence between simulated and observed data  shows that model misspecification is reduced by  restricting the reference substitutions to the disciplinary subnetwork (our model), as compared to treating all substitutions within WoS as equiprobable.
}
\label{tab:kld}
\centering
\begin{tabular}{| ccccc |} 
  \hline
 Disciplinary Network & Year & Background Network & K-L Divergence & Ratio \\ 
  \hline
 appl\_physics & 1985 & local & 1.21 &  \\ 
  & 1985 & global & 2.37 & 1.96 \\ 
  & 1995 & local & 0.86 &  \\ 
  & 1995 & global  & 2.37 & 2.77 \\ 
  & 2005 & local & 0.95 &  \\ 
  & 2005 & global  & 2.35 & 2.47 \\ 
    \hline
  immunology & 1985 & local & 0.75 &  \\ 
  & 1985 & global  & 1.68 & 2.24 \\ 
   & 1995 & local & 0.78 &  \\ 
   & 1995 & global  & 1.70 & 2.19 \\ 
   & 2005 & local & 0.73 &  \\ 
  & 2005 & global  & 1.92 & 2.63 \\ 
    \hline
 metabolism & 1985 & local & 1.11 &  \\ 
   & 1985 & global  & 2.24 & 2.02 \\ 
  & 1995 & local & 1.07 &  \\ 
  & 1995 & global  & 2.33 & 2.17 \\ 
     & 2005 & local & 1.19 &  \\ 
   & 2005 & global  & 2.60 & 2.18 \\ 
   \hline
\end{tabular}
\end{table}

 We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.  
 The results (Table \ref{tab:kld}) confirm this prediction: simulations 
under the constrained model consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable. 
\textcolor{blue}{
Furthermore, the K-L divergence for  the unconstrained model (background network all of WoS) is generally twice as large as the K-L divergence for the constrained models (where the background network is the local disciplinary subnetwork), with ratios that range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases.
These results clearly demonstrate that constraining reference substitutions to the given local disciplinary network better fits the observed data, so that there is reduced model misspecification.}

@@

Since the constrained model better fits the observed data, we evaluated the distribution of 
highly cited articles  (i.e., ``hit articles")
 in the four categories (HCHN, LCHN, HCLN, LCLN), for different
thresholds for hit articles.
Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category. 
The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency. 
However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),
and the highest hit rates for the 1995 applied physics datasets are in the 
HNLC category for both the top 1\% and top 10\% of all cited articles.  
%Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}). 
 Thus, the category exhibiting the highest hit rate among highly cited papers depends on the
specific disciplinary network and to some extent on the threshold for being highly cited.
 %was the case with immunology. 
Furthermore, the categories displaying the greatest hit rate vary 
to some extent % with parameter settings and 
with the year \textcolor{blue}{(data not shown)}.
%The lack of stable results across parameter settings suggests that parameters must be selected judiciously.

%\textcolor{blue}{I did not review the next two paragraphs.  I did--JRB}

@@

We also tested the explanatory power of each framework dimension by classifying articles as %Low Novelty (
LN %)
 or 
% High Novelty (
HN
%)
 and, separately, as 
% having Low Conventionality (
LC
%) 
or 
%High Conventionality (
HC. 
%)
We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.  That null hypothesis was rejected for the WoS data along both dimensions. Consistent with the findings in~\cite{uzzi_atypical_2013}, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and also overrepresented in the HN category at a $p<0.001$ in all but two cases: the p-values in those exceptions were $0.002$ and $0.007$.  
Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS. \textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  
In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.  Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$. These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, and (3) novelty is more strongly related with hits in applied physics than is conventionality. More generally, we find that the dimensions most strongly related with hit articles vary between disciplinary and broad data sets, and also among disciplines.

We described concerns with model misspecification along two general dimensions: the background dataset and sampling methodology for the random graph. The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology through the article z-score distributions. When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles. We thought it important to determine the extent to which each of our methodological differences contributed to our observations.  We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.  In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used.
% and x\% z-scores changed signs in the case of the immunology dataset. \textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} 
We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.

@@

%\emph{needs to be expanded}

\textcolor{blue}{
The fundamental difference between the Uzzi {\em et al.} model and ours is just one parameter--the set of references that can be used as substituents during the substitution process.
We provided several lines of evidence that showed that changing this one parameter from all of WoS to the local disciplinary subnetwork
%This study shows strong evidence that constraining the substitution model to the local disciplinary subnetwork 
reduces model misspecification. Furthermore,  using the constrained model (which allows substitutions only within the local subnetwork)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the subnetwork.}
 In particular, when using the unconstrained model, highly cited papers were most likely to be
in the HNHC category but this trend does not consistently hold when using the constrained model. Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research. 
In particular,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}). 
%\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} 
Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN. \textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.  
%However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.

\textcolor{blue}{
More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data and that is not robust to changes in thresholds for defining high impart articles or high novelty. 
%More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand. 
However, although  the constrained model reduces model misspecification compared to the unconstrained model,  this does not imply that the constrained model is reasonable nor that trends observed under the constrained model should be considered relevant to understanding scientific practice.
Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
}

\textcolor{blue}{
However, this study does suggest some directions for future work...
First, we do show that disciplinary behavior differs, so models based on individual disciplines
}
